Heavy inextensible strings in the Schwarzschild geometry

### 2024-10-31 weighted_string.Rmd
start documenting

>>>>

The light inextensible string functional was

$$
\int_{p_1}^{p_2}\left(\frac{\left(r'\right)^2}{1-2M/r} + r^2\right)^\frac{1}{2}d\phi
$$

But now we use a Lagrange multiplier:

$$
\int_{p_1}^{p_2}\left[\left(\frac{\left(r'\right)^2}{1-2M/r} + r^2\right)^\frac{1}{2}
+\lambda\left(\frac{\left(r'\right)^2}{1-2M/r} + r^2\right)^\frac{1}{2}
\left(1+\lambda(1-\sqrt{1-2M/r})\right)
\right]d\phi
$$

that is, miminizing the potential energy subject to a (proper) length
constraint.  Simplifying:

$$
\int_{p_1}^{p_2}\left(\frac{\left(r'\right)^2}{1-2M/r} +
r^2\right)^\frac{1}{2} \left(1+\lambda(1-\sqrt{1-2M/r})\right) d\phi
$$

```
EulerEquations[ 
  Sqrt[r[\[Phi]]^2 + 
     r'[\[Phi]]^2/(1 - 2*M/r[\[Phi]])]*(1 + \[Lambda]*(1 - 
        Sqrt[1 - 2*M/r[\[Phi]]])), r[\[Phi]], \[Phi]] // FullSimplify
```
